Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices

### 2018-05-22 Meetings/23.05.2018.mst1tfm/mst1tfm_topic21_vianello.tex
Update to figures for MST-TFM meeting and TeX files

\documentclass[10pt, compress]{beamer}
\usetheme[conference=Topic21-Analysis-Meeting,venue=Remote, date=17/05/2018, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{tangocolors}
\usepackage{rfxcolor}
\definecolor{colorA}{HTML}{324D5C}
\definecolor{colorB}{HTML}{E37B40}
\definecolor{colorC}{HTML}{60A65F}
% multiple figure location
%\graphicspath{{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/}{../Experiments/}}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{onimage}
\usepackage[export]{adjustbox}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{../biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Topic 21 Experiment and analysis}
\date{17 May 2018}
\author[N.Vianello]{presented by N. Vianello on behalf of  MST1-Topic 21
  scientific team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \centering{
  Volker Naulin, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov,
Jernej Kovacic, Benoît Labit, Bruce Lipschultz, 
Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente, 
Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
\end{frame}

@@

  \begin{itemize}
    \item \textbf{AUG:} Metallic wall, cryopumps, closed divertor with
      SP on vertical target, short divertor leg
    \item \textbf{TCV:} Carbon wall, completely open divertor,
      operated with relative long divertor leg, no cryopump  
  \end{itemize}
}
\only<2>{
  \vspace{-1.5cm}
  \centering{\includegraphics[width=0.7\textwidth]{../generalFigures/ProbeHead}}
\Fontvi
  \begin{itemize}
    \item \textbf{AUG:} Ion saturation current measured at different
      radial/poloidal position to get velocity from 2D cross-correlation
    \item \textbf{TCV:} Only 1 j$_{sat}$ measurement available,
      different velocity estimate. $v_r$ from
      $\mathbf{E}\times\mathbf{B}$ evaluation from floating potentials
      on CAS, $v_z$ from 2D cross-correlation analysis
  \end{itemize}
}
\only<3>{
  \centering{\includegraphics[width=0.7\textwidth]{../../Experiments/Comparison/pdfbox/ExampleCas}}
  \begin{itemize}
    \item Blob-size is $\delta_b = 0.5 * \tau_b*v_{\perp}$
    \item $\tau_b$ estimated from FWHM of Conditional Avearage
      (\alert{different from Carralero}) including asymmetric part
      (\alert{different from Tsui})
  \end{itemize}
}
\only<4>{
  \begin{columns}
    \begin{column}{0.5\textwidth}
  \includegraphics[width=\textwidth]{../../Experiments/Comparison/pdfbox/ExampleCorrelation}
    \end{column}
    \begin{column}{0.5\textwidth}
  \begin{itemize}
    \item Correlation on TCV computed using a gaussian Fit of the
      central part (better resolution)
    \item on AUG the correlation is in general asymmetric. Maximum
      time lag estimated from the zeros of the imaginary part of the
      hilbert transform of the correlation function
  \end{itemize}
    \end{column}
  \end{columns}
}

@@

          L$_{\parallel}$. There is a factor of 5 difference between

@@

          subdivertor region reached. NBI additional power added to

@@

        \item<5|only@5> Whenever considered as a a function of

@@

          almost reconciled for AUG \alert{but not for TCV}

@@

        \item<4|only@4> Again for AUG peak target density rollover

@@

          higher current whereas lower I$_p$ does not exhibit sign of

@@

          achieved. \alert{Consistent with lack of signature of

>>>>

\documentclass[10pt, compress]{beamer}
\usetheme[conference=MST1-TFM,venue=Padova, date=23/05/2018, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{tangocolors}
\usepackage{rfxcolor}
\definecolor{colorA}{HTML}{324D5C}
\definecolor{colorB}{HTML}{E37B40}
\definecolor{colorC}{HTML}{60A65F}

% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{onimage}
\usepackage[export]{adjustbox}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{../biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}
\date{23 May 2018}
\author[N.Vianello]{presented by N. Vianello on behalf of  MST1-Topic 21
  scientific team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \centering{
  Volker Naulin, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov,
Jernej Kovacic, Benoît Labit, Bruce Lipschultz, 
Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente, 
Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
\end{frame}

\begin{frame}{Background}
  \only<1>{
\begin{itemize}
\item Role of turbulence transport in the SOL saturation is a well
  know
  feature \parencite{LaBombard:2001ks,Rudakov:2005ic,Garcia:2007hh,Carralero:2014gs}. \textcolor{red}{Increasing
  density, even without reaching detachment SOL profile tend to flatten}
\end{itemize}}
% \only<2-3>{
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item Present understanding suggests that a transition of filament
%         propagation regime is dominated by effective
%         collisionality $\Lambda$ \parencite{Myra:2006p2754}
%         \begin{equation*}
%           \Lambda = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
%         \end{equation*}
%         \item<3> \textcolor{red}{At constant blob size, increasing
%             collisionality provide a change in the filaments velocity
%             scaling properties}
%       \end{itemize}
%     \end{column}
%     \begin{column}{0.5\textwidth}
% %      \includegraphics<2>[width=\textwidth]{../pdfbox/Presentation/FigMyra}
%         \begin{tikzonimage}[width=\textwidth]{../generalFigures/FigMyra}
%           \only<3>{
%             \draw [->, ultra thick, red] (0.7,0.3) -- (0.7,0.6);}
%         \end{tikzonimage}
%     \end{column}
%   \end{columns}
% }
\only<2-4>{
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item AUG and JET (HT) \parencite{Carralero:2015gu} suggest that $\Lambda_{div}=\frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}$ dominates this
        process and a transition from
        \textcolor{ta3chameleon}{sheath-limited}
        \onslide<3-4>{to \textcolor{blue}{inertial regime}} 
        \item<4> \textcolor{red}{Tested by changing n$_e$
            and $T_e$ through fueling/seeding/heating}
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{tikzonimage}[width=\textwidth]{../generalFigures/KoMFig2.png}
        \only<2-4>{
          \draw [thick, ta3chameleon, thick] (0.45,0.25) ellipse (0.23 and 0.1);
      }
        \only<3-4>{
          \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
      }
        \only<4>{
          \draw [thick, red, thick, dashed] (0.35,0.75) circle (0.25);
      }
    \end{tikzonimage}
  \end{column}
  \end{columns}
}
\only<5-7>{
  \begin{columns}[c]
    \begin{column}{0.4\textwidth}
      \begin{itemize}
      \item<5|only@5> $\Lambda_{div}$ does not describe properly evolution
        of upstream profile in JET-VT \parencite{Wynn:2018gp}
      \item<6-7> On TCV \parencite{Vianello:2017ku} $\Lambda_{div}$
        necessary but not sufficient to guarantee increase $\lambda_n$
        in the far SOL
      \item<7|only@7> Additional mechanism suggested among which
        \alert{neutral clogging} 
    \end{itemize}
  \end{column}
  \begin{column}{0.6\textwidth}
    \centering{\includegraphics<5>[width=\textwidth]{../generalFigures/Wynn-HT-VT}}
    \centering{\includegraphics<6-7>[width=\textwidth]{../generalFigures/Vianello-TCV}}
  \end{column}
\end{columns}
}
\centering{\includegraphics<1>[width=1.1\textwidth]{../generalFigures/Various-density-profiles}}
\end{frame}

@@

  \begin{itemize}
    \item \textbf{AUG:} Metallic wall, cryopumps, closed divertor with
      SP on vertical target, short divertor leg
    \item \textbf{TCV:} Carbon wall, completely open divertor,
      operated with relative long divertor leg, no cryopump  
  \end{itemize}
}
\only<2>{
  \vspace{-1.5cm}
  \centering{\includegraphics[width=0.7\textwidth]{../generalFigures/ProbeHead}}
\Fontvi
  \begin{itemize}
    \item \textbf{AUG:} Ion saturation current measured at different
      radial/poloidal position to get velocity from 2D cross-correlation
    \item \textbf{TCV:} Only 1 j$_{sat}$ measurement available,
      different velocity estimate. $v_r$ from
      $\mathbf{E}\times\mathbf{B}$ evaluation from floating potentials
      on CAS, $v_z$ from 2D cross-correlation analysis
  \end{itemize}
}
\only<3>{
  \centering{\includegraphics[width=0.7\textwidth]{../../Experiments/Comparison/pdfbox/ExampleCas}}
  \begin{itemize}
    \item Blob-size is $\delta_b = 0.5 * \tau_b*v_{\perp}$
    \item $\tau_b$ estimated from FWHM of Conditional Avearage
      binormal blob velocity estimated (although differently in the
      two devices)
  \end{itemize}
}
\end{frame}

@@

          L$_{\parallel}$ (shown from the X-point height to the outer
          target).
          There is a factor of 5 difference between

@@

          subdivertor region reached. 0.5 MW NBI additional power added to

@@

        \item<5|only@5> Whenever considered as a function of

@@

          almost reconciled for AUG \alert{but not for TCV and at 0.6
            MA for AUG}

@@

        \item<4|only@4> AUG peak target density rollover

@@

          higher current: \alert{lower I$_p$ does not exhibit sign of

@@

          achieved. Consistent with lower 
